### 2022-03-31 manuscript.tex
thursday [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/92ef2d831287c2ff7b407a0430e34b450ef9997c.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/92ef2d831287c2ff7b407a0430e34b450ef9997c/checks
https://github.com/scherzerthesis/thesis/actions/runs/2073477413

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/1af40d40f8291eb85788543d7614044c788929f1/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/1af40d40f8291eb85788543d7614044c788929f1}{scherzerthesis/thesis@1af40d4}
on March 30, 2022.

@@

@@

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/92ef2d831287c2ff7b407a0430e34b450ef9997c/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/92ef2d831287c2ff7b407a0430e34b450ef9997c}{scherzerthesis/thesis@92ef2d8}
on March 31, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgf1.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgf2.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_1.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

@@

\hypertarget{chapter-six-future}{%
\subsection{Chapter Six: Future}\label{chapter-six-future}}

\#\#Conclusions
The broad purpose of this work was to better understand how BRAF\textsuperscript{V600E} tumors form and progress to lung adenocarcinoma.
Our strategy was (1) to determine additional tumor supressor genes in BRAF\textsuperscript{V600E} lung tumorigenesis, (2) evaluate effect different mutant-p53 alleles, and (3) profile the tumor cell heterogenity using scRNA-seq.

\#\#Future directions
immuno profiling?
